### 2024-11-08 manuscript.tex
Add funding acks

PK and FB received funding from the European Union’s Horizon 2020 research and
innovation program under a grant agreement no. 101003470. Supercomputing
resources were provided by the DKRZ (project 1125 ICON-development) and the
National Academic Infrastructure for Supercomputing in Sweden (allocation
2023/22-202). We acknowledge the contribution of Thorsten Mauritsen to funding
acquisition and project management.  We acknowledge the RV \emph{Polarstern}
datasets provided by the Alfred Wegener Institute and Pangaea, the AA15-16
dataset provided by the Australian Antarctic Division (AAD) and University of
Canterbury (UC), RV \emph{Tangaroa} datasets provided by the National Institute
of Water and Atmospheric Research and UC, the NBP1704 dataset provided by the
National Science Foundation, Cooperative Institute for Research in
Environmental Sciences, University of Colorado and UC, the HMNZSW16 dataset
provided by the Royal New Zealand Navy and UC, the MARCUS dataset provided by
the Atmospheric Radiation Measurement (ARM) and AAD, and the MICRE dataset
provided by ARM, the Australian Bureau of Meteorology, and AAD. We thank the
scientific staff, the crew, and everyone involved in collecting data on the
voyages and stations, especially Gert König-Langlo, Holger Schmithüsen, Roger
Marchand, Peter Guest, Kelly Schick, Sally Garrett, Jamie Halla, and Mike J.
Harvey (†). We acknowledge the ICON model output provided by the nextGEMS
project, Deutscher Wetterdienst, Max-Planck-Institute for Meteorology, DKRZ,
Karlsruhe Institute of Technology, and Center for Climate Systems Modeling;
reanalysis dataset ERA5 provided by the Copernicus Climate Change Service;
MERRA-2 provided by the Global Modeling and Assimilation Office; CERES datasets
provided by the NASA Langley Atmospheric Science Data Center Distributed Active
Archive Center; and the Natural Earth dataset provided by naturalearthdata.com.
Last but not least, we acknowledge the use of open source software Python,
Cython \citep{behnel2011}, TensorFlow \citep{abadi2016}, Devuan GNU+Linux,
parallel \citep{tange2011}, NumPy \citep{harris2020}, SciPy
\citep{virtanen2020}, Matplotlib \citep{hunter2007}, cartopy \citep{cartopy},
pyproj, Inkscape, Bash, GNU Fortran, HDF \citep{folk1999}, and NetCDF
\citep{rew1990}.  We dedicate this study to the memory of Mike J.  Harvey, who
very substantially contributed to obtaining the atmospheric observations on the
RV \emph{Tangaroa} voyages used in this study.

>>>>

PK and FB, and the nextGEMS project received funding from the European Union’s
Horizon 2020 research and innovation program under a grant agreement no.
101003470. FB received funding from the Wenner-Gren foundation and the Swedish
e-Science Research Centre. Supercomputing resources were provided by the DKRZ
(project 1125 ICON-development) and the National Academic Infrastructure for
Supercomputing in Sweden (allocation 2023/22-202). The data collection by the
University of Canterbury was funded by the Deep South National Science
Challenge Clouds and Aerosols project.  Data collection on the RSV \emph{Aurora
Australis} was funded by the Australian Antarctic Science project (grant no.
4292).  We acknowledge the contribution of Thorsten Mauritsen to funding
acquisition and project management.  We acknowledge the RV \emph{Polarstern}
datasets provided by the Alfred Wegener Institute and Pangaea, the AA15-16
dataset provided by the Australian Antarctic Division (AAD) and University of
Canterbury (UC), RV \emph{Tangaroa} datasets provided by the National Institute
of Water and Atmospheric Research and UC, the NBP1704 dataset provided by the
National Science Foundation, Cooperative Institute for Research in
Environmental Sciences, University of Colorado and UC, the HMNZSW16 dataset
provided by the Royal New Zealand Navy and UC, the MARCUS dataset provided by
the Atmospheric Radiation Measurement (ARM) and AAD, and the MICRE dataset
provided by ARM, the Australian Bureau of Meteorology, and AAD. We thank the
scientific staff, the crew, and everyone involved in collecting data on the
voyages and stations, especially Gert König-Langlo, Holger Schmithüsen, Roger
Marchand, Peter Guest, Kelly Schick, Sally Garrett, Jamie Halla, Mike J.
Harvey (†). We thank Loretta Preis for providing additional RV
\emph{Polarstern} data.  We acknowledge the ICON model output provided by the
nextGEMS project, Deutscher Wetterdienst, Max-Planck-Institute for Meteorology,
DKRZ, Karlsruhe Institute of Technology, and Center for Climate Systems
Modeling; reanalysis dataset ERA5 provided by the Copernicus Climate Change
Service; MERRA-2 provided by the Global Modeling and Assimilation Office; CERES
datasets provided by the NASA Langley Atmospheric Science Data Center
Distributed Active Archive Center; and the Natural Earth dataset provided by
naturalearthdata.com.  Last but not least, we acknowledge the use of open
source software Python, Cython \citep{behnel2011}, TensorFlow
\citep{abadi2016}, Devuan GNU+Linux, parallel \citep{tange2011}, NumPy
\citep{harris2020}, SciPy \citep{virtanen2020}, Matplotlib \citep{hunter2007},
cartopy \citep{cartopy}, pyproj, Inkscape, Bash, GNU Fortran, HDF
\citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate this study to the
memory of Mike J.  Harvey, who very substantially contributed to obtaining the
atmospheric observations on the RV \emph{Tangaroa} voyages used in this study.
